Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-01 paper_jasa.tex
Cleaning up experimental results section

\subsection{Experiment with a discrete covariate}

@@

\subsection{Experiment with a continuous covariate}

@@

\subsection{Experiment with contaminated data}

>>>>

Three experiments were conducted to evaluate the effectiveness of the lineup protocol relative to the equivalent test statistic used in the regression scenario. There are three experiments. The first two are classical settings where we would not expect the lineup protocol to do better than the traditional test, but we hope it to perform favorably. The third experiment is a scenario where assumptions required for the traditional test are violated, and we would expect the lineup protocol to outperform the traditional test.

\subsection{Discrete covariate}

@@

\subsection{Continuous covariate}

@@

\subsection{Contaminated data}
